### 2020-03-14 paper/sections/evaluation.tex
change the figure format
improve consistency

We carry out real-world experiments to verify our solution's performance. We use a desktop PC with an NVIDIA 1080ti graphic card as the edge infrastructure. For the cloud deep learning services, we choose Baidu Vision, Face++ object detection services, and Amazon Rekognition. In the experiments, we use two datasets mentioned before in Sec.\ref{subsec:insight}, ImageNet dataset indicating daytime scenery and the FLIR Thermal Dataset indicating nighttime scenery. Some important hyperparameters in our experiments are given in Table \ref{tab: parameters}.

@@

We use the ImageNet dataset in size reduction and accuracy performance experiment, DeepN-JPEG comparative experiment, and end-to-end latency simulation. Moreover, we use ImageNet and the FLIR Thermal Dataset alternately to simulate the scenery change in the inference-estimation-querying-retraining mechanism experiment, and analyze the RL agent's best compression strategy selection in different input image sceneries.

@@

In our experiments, we measure the compressed and original image's file size to obtain the compression rate $ \Delta s $. Since we don't have the real ground truth label of an image, we use the output $ \vec{y}_{\rm ref} $ from a reference image as the ground truth label, and calculate the relative top-5 accuracy $ \mathcal{A} $ as the accuracy metric, the formula of $ \mathcal{A} $ is presented in Sec. ~\ref{subsec: formulation}.

\subsection{Upload Size Overhead}

@@

Figure \ref{fig: train_steps} presents the upload traffic load of the training and inference phase, to be more intuitionistic, we plot the size overhead $ \frac{s}{s_{\rm ref}} $ as the $ y $-axis where $ s $ is the real upload size of AdaCompress, $ s_{\rm ref} $ is the benchmark upload size. Therefore $ y \geq 1 $ means that our solution uploads more data then benchmark, and $ y < 1 $ means the compression rate of AdaCompress. From Figure \ref{fig: train_steps} we can see that as the training procedure runs, the upload size decreases because the RL agent learns to choose better compression quality levels to upload fewer data. In the training phase, to train the agent while remaining a convincing recognition result, we have to upload the original image to the cloud to get the real result, along with the compressed image to obtain reward feedback, therefore the upload traffic load is even higher than the conventional solution. But once the training phase has finished, the upload traffic load is much lower than the benchmark. As shown in Figure \ref{fig: compress_performance}, in the inference phase, AdaCompress's upload size is only 1/2 of the benchmark's. %% \\

@@

Figure \ref{fig: compress_performance} presents the compression performance in the inference phase for each cloud service. We test AdaCompress on Face++, Baidu Vision and Amazon Rekognition, comparing to the conventional compression level, for all tested cloud services, our solution can reduce the upload size by more than 1/2, meanwhile, the relative accuracy, indicated by brown bars, only decreases about 7\% on average, proving the efficiency of our design. %% \\

@@

\begin{figure}[htbp]
    \includegraphics[width=\linewidth]{figures/compare_DeepN.eps}
    \caption{Comparative compression performance between DeepN-JPEG and AdaCompress}
    \label{fig: compare_DeepN}
    % \vspace{-0.3cm}
\end{figure}

@@

Figure \ref{fig: compare_DeepN} presents a comparison performance between DeepN-JPEG and AdaCompress for each cloud service. As we can see, both DeepN-JPEG and AdaCompress cut down the upload size overhead more than 1/2. However, for all tested cloud services, AdaCompress's accuracy is higher than DeepN-JPEG's slightly. Compared with DeepN-JPEG's average accuracy is about 85\% on three cloud services, while AdaCompress achieves a better average accuracy of 93\%. In a word, comparing to the DeepN-JPEG framework, AdaCompress presents a similar upload traffic load reduction performance but achieving higher inference accuracy for computer vision cloud services.

AdaCompress compresses images in a more adaptive manner rather than DeepN-JPEG. (i.e., the explanation of why AdaCompress achieves a better accuracy). As shown in Figure \ref{fig: compare_image}, for picture 1a, compared to DeepN-JPEG, AdaCompress compresses the image at the compression quality level of 15, a more aggressive compression quality level to reduce upload size overhead. On the contrary, for picture 2a of Figure \ref{fig: compare_image}, DeepN-JPEG compresses the image with the same quantization table, but AdaComperss chooses a higher compression quality level to preserve more details so that the backend deep learning model can still recognize the picture. Being different from the DeepN-JPEG framework compresses all images with the same quantization table, our RL agent chooses a lower compression quality level for picture 1a and a relatively higher compression quality level for picture 2a based on the feature of the input image.

@@

Comparing to DeepN-JPEG, AdaCompress has three advantages and one disadvantage as following: %% \\    
    \begin{itemize}
        \item AdaCompress and DeepN-JPEG both decrease the upload size overhead more than 1/2, but AdaCompress maintains higher inference accuracy.
        \item DeepN-JPEG requires the original dataset information to redesign the quantization table, while AdaCompress chooses compression quality level adaptively without any pre-knowledge of the original dataset. 
        \item When the scenery changes, DeepN-JPEG still compresses images with the same quantization table, while AdaCompress's inference-estimation-querying-retraining mechanism captures the scenery change and invokes either model querying method or retraining kernel to generate a more suitable compression selection strategy for the current scenery.
        \item DeepN-JPEG redesigns the quantization table locally, while AdaCompress needs to upload origin images and compressed images to the cloud in the training phase, leading some upload size overhead at the beginning. 
    \end{itemize}

@@

To evaluate the efficiency of the inference-estimation-querying-retraining mechanism, we feed AdaCompress with a combined dataset whose first 2000 images from FLIR Thermal images, the later 3000 images randomly sampled from ImageNet, and the last 2000 images from FLIR Thermal images. We adapt AdaCompress's current RL agent to FLIR Thermal nighttime scenery by training it on the FLIR Dataset, and we run AdaCompress on the combined dataset, observing AdaCompress's behavior upon the scenery changes at step 2000 and 5000. %% \\

We illustrate AdaCompress's behavior in Figure \ref{fig: running-retrain}, the $ x $-axis indicates steps, the vertical red line means the dataset change (i.e. scenery change). We plot AdaCompress's overall accuracy as the green line and the estimation probability $ p_{\rm est} $ as the gray line. At the bottom of Figure \ref{fig: running-retrain}, we also plot the scaled upload size of AdaCompress and benchmark solution to illustrate the upload size overhead in the inference phase.
%with a $ \Delta $ mark on $ x $-axis

%\begin{figure}[htbp]
%    \includegraphics[width=\linewidth]{figures/running-retrain.pdf}
%    \caption{AdaCompress's reaction upon scenery change}
%%    \vspace{-0.2cm}
%    \label{fig: running-retrain}
%\end{figure}

\begin{figure}[htbp]
    \includegraphics[width=\linewidth]{figures/running-retrain.eps}
    \caption{AdaCompress's reaction upon scenery change}
    %    \vspace{-0.2cm}
    \label{fig: running-retrain}
\end{figure}

From Figure \ref{fig: running-retrain} we can see that AdaCompress can adaptively update the estimation probability $ p_{\rm est} $, usually, when the overall accuracy decreases, AdaCompress would increase the estimation probability, trying to capture the scenery change. When the overall accuracy is stable and high enough, the estimation probability $ p_{\rm est} $ decreases to reduce transmission. %% \\

Upon the first data scenery changes (i.e., night to day) shown as the first vertical red line in Figure \ref{fig: running-retrain}, comparing to the earlier steps, the accuracy decreases dramatically and therefore $ p_{\rm est} $ raises to determine whether the scenery changes. The accuracy keeps dropping in the following estimations, indicating that the current RL agent is no more suitable for the current input scenery. At the moment, AdaCompress should switch into the model querying state and reload a new RL agent model from the model caching library. However, there is no model except the current RL agent in the model caching library at that time. Therefore, AdaCompress starts to retrain at once, to adapt the RL agent into the current scenery. The retraining steps are shown as the light-blue region in Figure~\ref{fig: running-retrain}. In the retraining phase, AdaCompress always uses the reference image's prediction label $ \vec{y}_{\rm ref} $ as the output result, therefore the accuracy $ \mathcal{A} $ and $ p_{\rm est} $ are locked to 1. After finishing retraining the agent in the daytime scenery, the trained agent is cached in the model cachling library, and in the following iterations, sometimes the accuracy decreases accidentally, and the estimation probability $ p_{\rm est} $ also raises to get more samples. The accuracy is not lower than the accuracy threshold $ \mathcal{A}_0 $ , therefore the retraining phase would not be triggered again until the second data scenery changes. %% \\

Upon the second data scenery changes (i.e., day to night) shown as the second vertical red line in Figure \ref{fig: running-retrain}, like the first scenery change, the accuracy decreases and $ p_{\rm est} $ raises, indicating that the current RL agent is no more suitable again. AdaCompress switches into the model querying state at once and reloades a new RL agent model (i.e., the initial model trained on the FLIR Thermal images) from the model caching library. When using the new agent in this scenery, the accuracy stops decreasing and maintains above the accuracy threshold, indicating the current RL agent is suitable for the current scenery.  %% \\

From Figure \ref{fig: running-retrain} we can also observe the uploading file size overhead in different phases, in retraining phase, AdaCompress uploads more data than the conventional benchmark, but in inference phase, AdaCompress's upload size is only half of the benchmark's. Especially when the second data scenery changes, AdaCompress achieves a lower upload traffic load by loading a suitable RL agent model rather than retraining from scratch. %% \\

@@

We test the RL agent's inference time and compressed file size for batches of images, and simulate the latency of uploading such compressed images. We test the average inference latency on 1000 ImageNet images and simulate the network bandwidth as 27.64 Mbps according to the global average fixed broadband upload speed~\cite{speedtest} in Feb. 2019, to verify the end-to-end latency performance. The latency comparison is listed in Table \ref{tab: latency-overhead}. %% \\

>>>>

We carry out real-world experiments to verify our solution's performance. We use a desktop PC with an NVIDIA 1080ti graphic card as the edge infrastructure. For the cloud deep learning services, we choose Baidu Vision, Face++ object detection services, and Amazon Rekognition. In the experiments, we use two datasets mentioned before in Sec.~\ref{subsec:insight}, ImageNet dataset indicating daytime scenery and the FLIR Thermal Dataset indicating nighttime scenery. Some important hyperparameters in our experiments are given in Table ~\ref{tab: parameters}.

@@

We use the ImageNet dataset in size reduction and accuracy performance experiment, DeepN-JPEG comparative experiment, and end-to-end latency simulation. Moreover, we use ImageNet and the FLIR Thermal Dataset alternately to simulate the scenery change in the \emph{inference-estimation-querying-retraining} mechanism experiment, and analyze the RL agent's best compression strategy selection in different input image ``sceneries''.

@@

In our experiments, we measure the compressed and original image's file size to obtain the compression rate $ \Delta s $. Since we don't have the real ground truth label of an image, we use the output $ \vec{y}_{\rm ref} $ from a reference image as the ground truth label, and calculate the relative top-5 accuracy $ \mathcal{A} $ as the accuracy metric, the formula of $ \mathcal{A} $ is presented in Sec.~\ref{subsec: formulation}.

\subsection{Upload Image Size Overhead}

@@

Figure~\ref{fig: train_steps} presents the upload traffic load of the training and inference phase, to be more intuitionistic, we plot the size overhead $ \frac{s}{s_{\rm ref}} $ as the $ y $-axis where $ s $ is the real upload size of AdaCompress, $ s_{\rm ref} $ is the benchmark upload size. Therefore $ y \geq 1 $ means that our solution uploads more data then benchmark, and $ y < 1 $ means the compression rate of AdaCompress. From Figure~\ref{fig: train_steps} we can see that as the training procedure runs, the upload image size decreases because the RL agent learns to choose better compression quality levels to upload fewer data. In the training phase, to train the agent while remaining a convincing recognition result, we have to upload the original image to the cloud to get the real result, along with the compressed image to obtain reward feedback, therefore the upload traffic load is even higher than the conventional solution. But once the training phase has finished, the upload traffic load is lower than the benchmark. As shown in Figure~\ref{fig: compress_performance}, in the inference phase, AdaCompress's upload size is only 1/2 of the benchmark's. %% \\

@@

Figure~\ref{fig: compress_performance} presents the compression performance in the inference phase for each cloud service. We test AdaCompress on Face++, Baidu Vision and Amazon Rekognition, comparing to the conventional compression level, for all tested cloud services, our solution can reduce the upload size by more than 1/2, meanwhile, the relative accuracy, indicated by brown bars, only decreases about 7\% on average, proving the efficiency of our design. %% \\

@@

\begin{figure}[htbp]
    \includegraphics[width=\linewidth]{figures/compare_DeepN.pdf}
    \caption{Comparative compression performance between DeepN-JPEG and AdaCompress}
    \label{fig: compare_DeepN}
    % \vspace{-0.3cm}
\end{figure}

@@

Figure~\ref{fig: compare_DeepN} presents a comparison performance between DeepN-JPEG and AdaCompress for each cloud service. As we can see, both DeepN-JPEG and AdaCompress cut down the upload size overhead more than 1/2. However, for all tested cloud services, AdaCompress's accuracy is higher than DeepN-JPEG's slightly. Compared with DeepN-JPEG's average accuracy is about 85\% on three cloud services, while AdaCompress achieves a better average accuracy of 93\%. In a word, comparing to the DeepN-JPEG framework, AdaCompress presents a similar upload traffic load reduction performance but achieving higher inference accuracy for online computer vision-based services.

AdaCompress compresses images in a more adaptive manner rather than DeepN-JPEG. (i.e., the explanation of why AdaCompress achieves a better accuracy). As shown in Figure~\ref{fig: compare_image}, for picture 1a, compared to DeepN-JPEG, AdaCompress compresses the image at the compression quality level of 15, a more aggressive compression quality level to reduce upload size overhead. On the contrary, for picture 2a of Figure~\ref{fig: compare_image}, DeepN-JPEG compresses the image with the same quantization table, but AdaComperss chooses a higher compression quality level to preserve more details so that the backend deep learning model can still recognize the picture. Being different from the DeepN-JPEG framework compresses all images with the same quantization table, our RL agent chooses a lower compression quality level for picture 1a and a relatively higher compression quality level for picture 2a based on the feature of the input image.

@@

Comparing to DeepN-JPEG, AdaCompress has three advantages and one disadvantage as following: %% \\    
    \begin{itemize}
        \item AdaCompress and DeepN-JPEG both decrease the upload size overhead more than 1/2, but AdaCompress maintains higher inference accuracy.
        \item DeepN-JPEG requires the original dataset information to re-design the quantization table, while AdaCompress chooses compression quality level adaptively without any pre-knowledge of the original dataset. 
        \item When the scenery changes, DeepN-JPEG still compresses images with the same quantization table, while AdaCompress's \emph{inference-estimation-querying-retraining} mechanism captures the scenery change and invokes either model querying method or retraining kernel to \emph{generate} a more suitable compression selection strategy for the current scenery.
        \item DeepN-JPEG re-designs the quantization table \emph{locally}, while AdaCompress needs to upload origin images and compressed images to the cloud in the training phase, leading some upload size overhead at the beginning. 
    \end{itemize}

@@

To evaluate the efficiency of the \emph{inference-estimation-querying-retraining} mechanism, we feed AdaCompress with a combined dataset whose first 2000 images from FLIR Thermal images, the later 3000 images randomly sampled from ImageNet, and the last 2000 images from FLIR Thermal images. We adapt AdaCompress's current RL agent to FLIR Thermal nighttime scenery by training it on the FLIR dataset, and we run AdaCompress on the combined dataset, observing AdaCompress's behavior upon the scenery changes at step 2000 and 5000. %% \\

We illustrate AdaCompress's behavior in Figure~\ref{fig: running-retrain}, the $ x $-axis indicates steps, the vertical red line means the dataset change (i.e. scenery change). We plot AdaCompress's overall accuracy as the green line and the estimation probability $ p_{\rm est} $ as the gray line. At the bottom of Figure~\ref{fig: running-retrain}, we also plot the scaled upload size of AdaCompress and benchmark solution to illustrate the upload size overhead in the inference phase.
%with a $ \Delta $ mark on $ x $-axis

%\begin{figure}[htbp]
%    \includegraphics[width=\linewidth]{figures/running-retrain.pdf}
%    \caption{AdaCompress's reaction upon scenery change}
%%    \vspace{-0.2cm}
%    \label{fig: running-retrain}
%\end{figure}
\begin{figure}[H]
    \includegraphics[width=\linewidth]{figures/running-retrain.pdf}
    \caption{AdaCompress's reaction upon scenery change}
    %    \vspace{-0.2cm}
    \label{fig: running-retrain}
\end{figure}

From Figure~\ref{fig: running-retrain} we can see that AdaCompress can adaptively update the estimation probability $ p_{\rm est} $, usually, when the overall accuracy decreases, AdaCompress would increase the estimation probability, trying to capture the scenery change. When the overall accuracy is stable and high enough, the estimation probability $ p_{\rm est} $ decreases to reduce transmission. %% \\

Upon the first data scenery changes (i.e., night to day) shown as the first vertical red line in Figure~\ref{fig: running-retrain}, comparing to the earlier steps, the accuracy decreases dramatically and therefore $ p_{\rm est} $ raises to determine whether the scenery changes. The accuracy keeps dropping in the following estimations, indicating that the current RL agent is no more suitable for the current input scenery. At the moment, AdaCompress should switch into the model querying state and re-load a new RL agent model from the model caching library. However, there is no model except the current RL agent in the model caching library at that time. Therefore, AdaCompress starts to re-train at once, to adapt the RL agent into the current scenery. The re-training steps are shown as the light-blue region in Figure~\ref{fig: running-retrain}. In the re-training phase, AdaCompress uses the reference image's prediction label $ \vec{y}_{\rm ref} $ as the output result, therefore the accuracy $ \mathcal{A} $ and $ p_{\rm est} $ are locked to 1. After finishing re-training the agent in the daytime scenery, the trained agent is cached in the model cachling library, and in the following iterations, sometimes the accuracy decreases accidentally, and the estimation probability $ p_{\rm est} $ also raises to get more samples. The accuracy is not lower than the accuracy threshold $ \mathcal{A}_0 $ , therefore the re-training phase would not be triggered again until the second data scenery changes. %% \\

Upon the second data scenery changes (i.e., day to night) shown as the second vertical red line in Figure~\ref{fig: running-retrain}, like the first scenery change, the accuracy decreases and $ p_{\rm est} $ raises, indicating that the current RL agent is no more suitable again. AdaCompress switches into the model querying state at once and re-loades a new RL agent model (i.e., the initial model trained on the FLIR Thermal images) from the model caching library. When using the new agent in this scenery, the accuracy stops decreasing and maintains above the accuracy threshold, indicating the current RL agent is suitable for the current scenery.  %% \\

From Figure~\ref{fig: running-retrain} we can also observe the uploading file size overhead in different phases, in re-training phase, AdaCompress uploads more data than the conventional benchmark, but in inference phase, AdaCompress's upload size is only half of the benchmark's. Especially when the second data scenery changes, AdaCompress achieves a lower upload traffic load by loading a suitable RL agent model rather than re-training from scratch. %% \\

@@

We test the RL agent's inference time and compressed file size for batches of images, and simulate the latency of uploading such compressed images. We test the average inference latency on 1000 ImageNet images and simulate the network bandwidth as 27.64 Mbps according to the global average fixed broadband upload speed~\cite{speedtest} in Feb. 2019, to verify the end-to-end latency performance. The latency comparison is listed in Table~\ref{tab: latency-overhead}. %% \\

### 2020-03-14 paper/sections/introduction.tex
improve consistency

\IEEEPARstart{W}{ith} the great success of deep learning in computer vision, this decade has witnessed an explosion of deep learning based computer vision applications. Because of the huge computational resource consumption for deep learning applications (e.g., inferring an image on VGG19 \cite{VGG19} requires $20$ GFLOPs of GPU resource), in today's computer vision applications, users usually have to upload the input images to the central cloud service providers (e.g., SenseTime, Baidu Vision and Google Vision, etc.), leading to a significant upload traffic load.

To reduce the upload traffic load, it is straightforward that an image should be compressed before one uploads it. Though JPEG has been used as the {\em de facto} image compression and encapsulation method, its performance for the deep computer vision models is not satisfactory. Liu et al.~\cite{DeepN-JPEG} showed that by redesigning the \emph{quantization table} in the default JPEG configuration, one can compress an image to a smaller version while maintaining the same inference accuracy for a deep computer vision model. However, such quantization solutions usually assume the inference model is fixed.

We then raise an intuitive question: to make it practically useful, can we select the JPEG configuration adaptively for different cloud computer vision services, without any prior knowledge of the original model and input images? In this paper, we propose a reinforcement learning based framework to select JPEG configurations adaptively. In our solution, we tackle the following design challenges.

@@

\item \emph{Lack of information about the cloud computer vision models.} Previous studies \cite{DeepN-JPEG,torfason2018towards,gueguen2018faster}, generally assume that the details of the computer vision models are available so that they can adjust the JPEG configuration according to the model structure, e.g., one can train a model to determine the JPEG configuration by plugging the original computer vision model into it. However, the structure details of online cloud computer vision models are usually proprietary and not open to the users.

\item \emph{Different cloud computer vision models need different JPEG configurations.} As an adaptive JPEG configuration solution, we target to provide a solution that is adaptive to different cloud computer vision services, i.e., it can \emph{generate} JPEG configuration for different models. However, today's cloud computer vision algorithms, based on deep and convolutional computations, are quite hard to understand. The same compression quality level could lead to a totally different accuracy performance. Some examples are shown in Figure \ref{fig: compress_accuracy}: picture 1a and 1b, 2a and 2b are visually similar for human beings, but the deep learning models give different inference results, only because they are compressed at different quality levels. And such a relationship is not apparent, e.g., picture 3b is highly compressed and looks destroyed comparing to picture 3a, but the deep learning model can still recognize it. This phenomenon is also presented in~\cite{delac2005effects} and commonly seen in adversarial neural network researches~\cite{yuan2019adversarial, evtimov2018robust}.

@@

To address the above challenges, we present a reinforcement learning based solution, called AdaCompress\footnote{We open-sourced AdaCompress that works with online computer vision APIs at \url{https://github.com/hosea1008/AdaCompress}}, to choose the proper compression quality level for an image to a computer vision model on the cloud, in an online manner. This paper is an extension of our earlier conference paper \cite{2019adacompress}, with the following contributions:

$\rhd$ We design an interactive training environment that can be applied to different computer vision cloud services. We propose a Deep Q-learning Network based agent to evaluate and predict the performance of a compression quality level on an input image. In real-world application scenarios, this agent can be highly efficient to run on today's edge infrastructures (e.g., Google edge TPU \cite{google-tpu}, Huawei Atlas 500 edge station \cite{huawei-atlas500}).

$\rhd$ We build a reinforcement learning framework to train the agent in the above environment. The agent can learn to choose a proper compression quality level for an input image after iteratively interacting with the environment by feeding the carefully designed reward that considers both accuracy and data size. Based on \cite{2019adacompress}, we further propose an \emph{explore-exploit} mechanism let the agent switch between ``sceneries''. In particular, after deploying the agent, an \emph{inference-estimate-retrain} solution is designed to restart the training once the scenery changes and the existing running agent cannot guarantee the original accuracy performance.

$\rhd$ In this journal extension, we provide more analysis and insights on our design. By analyzing the Q network's behaviors using Grad-Cam \cite{grad-cam}, we provide the reasons that the Q network chooses a specific compression quality level. We reveal that images containing large smooth areas are more sensitive to compression, while images with complex textures are more robust to compression for computer vision models.

$\rhd$ We evaluate our system on representative cloud deep learning services, including Amazon Rekognition \cite{amazon_rekognition}, Face++ \cite{face++_service} and Baidu Vision \cite{baidu_vision}, and show that our design can reduce the upload traffic load by up to $1/2$ while maintaining comparable overall accuracy. Compared to baseline DeepN-JPEG \cite{DeepN-JPEG}, the inference accuracy of AdaCompress is $8\%$ higher when they have similar compressed image size.

% \begin{itemize}
% 	\item First, we completed designing agent caching strategy work mentioned in our previous version's future work \cite{2019adacompress}, adding the model query state in previous inference-estimate-retrain mechanism to avoid unnecessary upload traffic load in the retraining phase. Once capturing the scenery change, comparing to the previous mechanism that retrains from scratch directly, in our new mechanism, AdaCompress switches into model query state and loads a suitable RL agent model, achieving a lower upload traffic load. In the experiment, we use the FLIR Thermal Dataset instead of the previous DNIM Dataset to act as a nighttime scenery since thermal sensors capture gray-scaled thermal images in the nighttime, and the experiment result shows that our design can cut down the uploading file size overhead effectively.
% 	\item Second, for the comparison purpose, we implement the DeepN-JPEG framework according to \cite{DeepN-JPEG} and evaluate the size reduction and accuracy performance. Our experiment shows that AdaCompress and DeepN-JPEG both decrease the uploading file size overhead more than 1/2, but the inference accuracy of AdaCompress is 8\% higher than that of DeepN-JPEG. Moreover, we provide illustrative image examples to present that AdaCompress compresses images more adaptively to achieve higher accuracy.
% 	\item Last but not least, we re-organize and amend the manuscript significantly to be easier to follow.
% \end{itemize}

The rest of this paper is organized as follows. We discuss related works in Sec.~\ref{sec: related_works}. In Sec.~\ref{sec: design} we present our framework and detailed design. We present our solution's performance in Sec.~\ref{sec: evaluation} and conclude the paper in Sec.~\ref{sec: conclusion}.

>>>>

\IEEEPARstart{W}{ith} the great success of deep learning in computer vision, this decade has witnessed an explosion of deep learning-based computer vision-based applications. Because of the huge computational resource consumption for deep learning applications (e.g., inferring an image on VGG19~\cite{VGG19} requires $20$ GFLOPs of GPU resource), in today's online computer vision-based applications, users usually have to upload the input images to the central cloud service providers (e.g., SenseTime, Baidu Vision and Google Vision, etc.), leading to a significant upload traffic load.

To reduce the upload traffic load, it is straightforward that an image should be compressed before one uploads it. Though JPEG has been used as the \emph{de facto} image compression and encapsulation method, its performance for the deep computer vision models is not satisfactory. Liu et al.~\cite{DeepN-JPEG} showed that by re-designing the quantization table in the default JPEG configuration, one can compress an image to a smaller version while maintaining the same inference accuracy for a deep computer vision model. However, such quantization solutions usually assume the inference model is fixed.

We then raise an intuitive question: to make it practically useful, can we select the JPEG configuration adaptively for different online computer vision-based services, without any prior knowledge of the original model and input images? In this paper, we propose a reinforcement learning-based framework to select JPEG configurations adaptively. In our solution, we tackle the following design challenges.

@@

\item \emph{Lack of information about the cloud-based computer vision models.} Previous studies~\cite{DeepN-JPEG, torfason2018towards, gueguen2018faster}, generally assume that the details of the computer vision models are available so that they can adjust the JPEG configuration according to the model structure, e.g., one can train a model to determine the JPEG configuration by plugging the original computer vision model into it. However, the structure details of online computer vision models are usually proprietary and not open to the users.

\item \emph{Different cloud-based computer vision models need different JPEG configurations.} As an adaptive JPEG configuration solution, we target to provide a solution that is adaptive to different online computer vision-based services, i.e., it can \emph{generate} JPEG configuration for different models. However, today's cloud-based computer vision algorithms, based on deep and convolutional computations, are quite hard to understand. The same compression quality level could lead to a totally different accuracy performance. Some examples are shown in Figure~\ref{fig: compress_accuracy}: picture 1a and 1b, 2a and 2b are visually similar for human beings, but the deep learning model gives different inference results, only because they are compressed at different quality levels. And such a relationship is not apparent, e.g., picture 3b is highly compressed and looks destroyed comparing to picture 3a, but the deep learning model can still recognize it. This phenomenon is also presented in~\cite{delac2005effects} and commonly seen in adversarial neural network researches~\cite{yuan2019adversarial, evtimov2018robust}.

@@

To address the above challenges, we present a reinforcement learning-based solution, called AdaCompress\footnote{We open-sourced AdaCompress that works with online computer vision-based APIs at \url{https://github.com/hosea1008/AdaCompress}}, to choose the proper compression quality level for an image to a computer vision model on the cloud, in an online manner. This paper is an extension of our earlier conference paper~\cite{2019adacompress}, with the following contributions:

$\rhd$ We design an interactive training environment that can be applied to different online computer vision-based services. We propose a Deep Q-learning Network-based~\cite{DQN} agent to evaluate and predict the performance of a compression quality level on an input image. In real-world application scenarios, this agent can be highly efficient to run on today's edge infrastructures (e.g., Google edge TPU~\cite{google-tpu}, Huawei Atlas 500 edge station~\cite{huawei-atlas500}).

$\rhd$ We build a reinforcement learning-based framework to train the agent in the above environment. The agent can learn to choose a proper compression quality level for an input image after iteratively interacting with the environment by feeding the carefully designed reward that considers both accuracy and data size. Based on~\cite{2019adacompress}, we further propose an \emph{explore-exploit} mechanism to let the agent switch between ``sceneries''. In particular, after deploying the agent, an \emph{inference-estimate-retrain} solution is designed to restart the training once the scenery changes and the existing running agent cannot guarantee the original accuracy performance.

$\rhd$~~In this journal extension, we provide more analysis and insights on our design. By analyzing the Deep Q-learning Network-based agent's behaviors using Grad-Cam~\cite{grad-cam}, we provide the reasons that the agent chooses a specific compression quality level. We reveal that images containing large smooth areas are more sensitive to compression, while images with complex textures are more robust to compression for computer vision models.

$\rhd$ We evaluate our system on representative cloud deep learning services, including Amazon Rekognition~\cite{amazon_rekognition}, Face++~\cite{face++_service} and Baidu Vision~\cite{baidu_vision}, and show that our design can reduce the upload traffic load by up to $1/2$ while maintaining comparable overall accuracy. Compared to baseline DeepN-JPEG~\cite{DeepN-JPEG}, the overall accuracy of AdaCompress is $8\%$ higher when they have similar compressed image size.

% \begin{itemize}
% 	\item First, we completed designing agent caching strategy work mentioned in our previous version's future work~\cite{2019adacompress}, adding the model query state in previous inference-estimate-retrain mechanism to avoid unnecessary upload traffic load in the retraining phase. Once capturing the scenery change, comparing to the previous mechanism that retrains from scratch directly, in our new mechanism, AdaCompress switches into model query state and loads a suitable RL agent model, achieving a lower upload traffic load. In the experiment, we use the FLIR Thermal Dataset instead of the previous DNIM Dataset to act as a nighttime scenery since thermal sensors capture gray-scaled thermal images in the nighttime, and the experiment result shows that our design can cut down the uploading file size overhead effectively.
% 	\item Second, for the comparison purpose, we implement the DeepN-JPEG framework according to~\cite{DeepN-JPEG} and evaluate the size reduction and accuracy performance. Our experiment shows that AdaCompress and DeepN-JPEG both decrease the uploading file size overhead more than 1/2, but the inference accuracy of AdaCompress is 8\% higher than that of DeepN-JPEG. Moreover, we provide illustrative image examples to present that AdaCompress compresses images more adaptively to achieve higher accuracy.
% 	\item Last but not least, we re-organize and amend the manuscript significantly to be easier to follow.
% \end{itemize}
The rest of this paper is organized as follows. We discuss related works in Sec.~\ref{sec: related_works}. In Sec.~\ref{sec: design} we present our framework and detailed design. We present our solution's performance in Sec.~\ref{sec: evaluation} and conclude the paper in Sec.~\ref{sec: conclusion}.
